Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-30 demystify.tex
updates

\begin{commentbox}[Didier]
  \emph{Should letter writers have PhDs?}  In Rwanda, a lot of students interact more with teaching faculty who might not have PhD.
  \tcblower
  \textbf{Vu}: This is an interesting and useful detail that US faculty might not be aware of and students should mention this in their statements. In general, someone with a PhD has been through the research process and therefore can better evaluate your research ability.  But if you do not have such people, then someone who can properly evaluate your research ability is still OK.
\end{commentbox}

>>>>

\begin{commentbox}[Didier]
  \emph{Should letter writers have PhDs?}  In Rwanda, a lot of students interact more with teaching faculty who might not have PhD.
  \tcblower
  \textbf{Vu}: This is an interesting and useful detail that US faculty might not be aware of. Students should mention this in their statements. In general, someone with a PhD has been through the research process and therefore can better evaluate your research ability.  But if you do not have such people, then someone who can properly evaluate your research ability is still OK (and again, explain that in your SOP).
\end{commentbox}
